Bird beak's elaboration and exploration

### 2021-09-28 Analysis/03-elaboration_exploration_analyses.Rmd
Update 03-elaboration_exploration_analyses.Rmd

```{r, fig.height = 6, fig.width = 18, echo = FALSE, eval = TRUE}
## Run the analyses of groups on the phylogeny
results_phylo <- covar.projections.wrapper(covar_matrices,
                                            type = "within",
                                            base = "phylogeny",
                                            dispRity.out = TRUE)
## Plot the results
wrap.plot(results_phylo,
          col = colour_vector[-4],
          main = "Projection on the\nglobal phylogeny axes")
```
Figure: the projection of each species per group onto the posterior distribution of global major phylogenetic axis.

>>>>

```{r, fig.height = 6, fig.width = 18, echo = FALSE, eval = TRUE}
## Run the analyses of groups on the phylogeny
results_phylo <- covar.projections.wrapper(covar_matrices,
                                            type = "within",
                                            base = "phylogeny",
                                            dispRity.out = TRUE)
## Plot the results
wrap.plot(results_phylo,
          col = colour_vector[-4],
          main = "Projection on the\nglobal phylogeny axes")

source("../Functions/circular.plot.R")

circular.plot.phytools(data = results_phylo$position, tree = demo_tree, gradient = c("blue", "orange"), clade.names = TRUE, clades = colour_vector[-4], lwd = 3)

```
Figure: the projection of each species per group onto the posterior distribution of global major phylogenetic axis.
